-Data improt-
 
```{r}
read_csv("a,b,c
1,2,3
4,5,6")
```

Sometimes there are a few lines of metadata at the top of the file. You can use skip = n to skip the first n lines; or use comment = "#" to drop all lines that start with (e.g.) #.  


```{r}
read_csv("The first line of metadata
  The second line of metadata
  x,y,z
  1,2,3", skip = 2)
```
 
   
```{r}
read_csv("# A comment I want to skip
  x,y,z
  1,2,3", comment = "#")
```
   
  he data might not have column names. You can use col_names = FALSE to tell read_csv() not to treat the first row as headings, and instead label them sequentially from X1 to Xn:
  
```{r}
read_csv("1,2,3\n4,5,6", col_names = FALSE)
```

 Alternatively you can pass col_names a character vector which will be used as the column names: 
 
 
```{r}
read_csv("1,2,3\n4,5,6", col_names = c("x", "y", "z"))
```
 
     Another option that commonly needs tweaking is na: this specifies the value (or values) that are used to represent missing values in your file:
     
 
```{r}
read_csv("a,b,c\n1,2,.", na = ".")
```
 
 This is all you need to know to read ~75% of CSV files that you’ll encounter in practice. You can also easily adapt what you’ve learned to read tab separated files with
 
 
 read_tsv() and fixed width files with read_fwf(). To read in more challenging files, you’ll need to learn more about how readr parses each column, turning them into R vectors.
    
    
    
    
 
```{r}
str(parse_logical(c("TRUE", "FALSE", "NA")))
```
 
```{r}
str(parse_integer(c("1", "2", "3")))
```

 
```{r}
str(parse_date(c("2010-01-01", "1979-10-14")))
```
 
 
```{r}
parse_integer(c("1", "231", ".", "456"), na = ".")
```
 
    
    
```{r}
x <- parse_integer(c("123", "345", "abc", "123.45"))
```
    
```{r}
x
```
    
```{r}
problems(x)
```
    
  
```{r}
parse_number("$123,456,789")
```
  
  
```{r}
parse_number("123.456.789", locale = locale(grouping_mark = "."))
```
  
  
```{r}
parse_number("123'456'789", locale = locale(grouping_mark = "'"))
```
  
  
```{r}
charToRaw("Hadley")
```
  
  
```{r}
x1 <- "El Ni\xf1o was particularly bad this year"

parse_character(x1, locale = locale(encoding = "Latin1"))

parse_character(x2, locale = locale(encoding = "Shift-JIS"))
```

  
```{r}
x2 <- "\x82\xb1\x82\xf1\x82\xc9\x82\xbf\x82\xcd"
 parse_character(x2, locale = locale(encoding = "Shift-JIS"))
```
  
  
  
  
```{r}
guess_encoding(charToRaw(x1))
```
  
  
```{r}
guess_encoding(charToRaw(x2))
```

```{r}
fruit <- c("apple", "banana")
parse_factor(c("apple", "banana", "bananana"), levels = fruit)
```
  




```{r}
parse_datetime("2010-10-01T2010")
```


```{r}
library(hms)
```

```{r}
parse_time("01:10 am")
```



-Problems- 


```{r}
challenge <- read_csv(readr_example("challenge.csv"))
```

```{r}
problems(challenge)
```

```{r}
tail(challenge)
```

```{r}
challenge <- read_csv(
  readr_example("challenge.csv"), 
  col_types = cols(
    x = col_double(),
    y = col_logical()
  )
)
```
Then you can fix the type of the y column by specifying that y is a date column:



```{r}
challenge <- read_csv(
  readr_example("challenge.csv"), 
  col_types = cols(
    x = col_double(),
    y = col_date()
  )
)
tail(challenge)
```
  


```{r}
challenge2 <- read_csv(readr_example("challenge.csv"), guess_max = 1001)
```


```{r}
challenge2
```












